GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-10-09 paper/kbanotebook2013/content/introduction.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass

In this article we describe the approach the GatorDSR team from 
University of Florida has adopted in addressing the challenge at NIST’s Text 
REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013. There are two main sections designed for this track. Cumulative Citation Recommendation and Streaming Slot Filling. Due to the importance of knowledgebases, both of these tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
Below we describe each of these tracks and their purposes in full detail.

An important challenge in maintaining Wikipedia.org (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate. Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation. As an example, the median time lag for a sample of about 60,000 web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail\cite{JFrank12}. It is also noted that the majority of Wikipedia entities have updates on their associated Wiki article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB. Further, the number of mentions is much larger than the number of entities\cite{JFrank12}.

@@

For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}. Documents would be divided according to two metrics: a) mentioning the entity or not, b) relevance level to the entity:
\begin{itemize}
\item \textbf{Mention} 
\begin{itemize}
\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
\item \textbf{Zero-mention:} Document does not directly mention target. Could still be relevant, e.g. metonymic references like ``this administration'' -- \textgreater ``Obama''. See also synecdoche. A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
\end{itemize}
\item \textbf{Relevance}
\begin{itemize}
\item \textbf{Garbage:} not relevant, e.g. spam.
\item \textbf{Neutral:} Not relevant, i.e. no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
impact on entity.
\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
central figure in topics/events.

@@

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain WP or Twitter entities 
(wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia 
or even fill-in the information boxes at Wikipedia. Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:

@@

\noindent In \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values. This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.

>>>>

An important challenge in maintaining Wikipedia.org (WP), the most popular 
web-based, collaborative, multilingual encyclopedia in the internet, is to 
make sure its contents are up-to-date. Presently, there is considerable time lag 
between the publication date of cited news and the date of an edit to WP 
creating the citation. The median time lag for a sample of about 60K
web pages cited by WP articles in the \textit{living\_people} category is over 
a year and the distribution has a long and heavy tail~\cite{JFrank12}. 
Also, the majority of WP entities have updates on their associated article much 
less frequently than their mention frequency. Such stale entries 
are the norm in any large knowledge base (KB) because the number of humans 
maintaining the KB is far fewer than the number of entities. 
%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful it users.

Given a set of entities, possible citations may come from a large variety of sources.
To attack this problem we develop a system to read streaming data and
filter out articles that are candidates for citations.
Given these documents, we extract the pairs of information in the 
article that is recommended for citations.

Our system contains three main components. First, we pre-process the data and
build models representing the knowledge base entries.
Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations.
Lastly, we processes sentences from candidate extractions and return 
specific information to be cited.

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
The data set from this task drop most our our design systems.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we built a system to filter a large amount of diverse documents (Section~\ref{},\ref{});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{},\ref{});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{},\ref{}).
\end{itemize}

\section{KBA Task Background\ceg{Move this to appendix?}}
\label{sec:kbatask}
The National Institute of Standards (NIST) hosted the
Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
contains two main sections designed for this track, Cumulative Citation Recommendation 
and Streaming Slot Filling. Due to the importance of knowledgebases, both of these 
tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
Below we describe each of these tracks and their purposes.

@@

For this track, assessors were instructed to ``use the Wikipedia article to 
identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
Documents would be divided according to two metrics: a) mentioning the entity or 
not, b) relevance level to the entity:
\begin{itemize}
  \item \textbf{Mention} 
    \begin{itemize}
      \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
        name, partial name, nickname, pseudonym, title, stage name.
      \item \textbf{Zero-mention:} Document does not directly mention target. Could 
        still be relevant, e.g.\ metonymic references like ``this administration'' --
        \textgreater ``Obama''. See also synecdoche. A document could also be relevant to 
        target entity through relation to entities mentioned in document -- apply this 
        test question: can I learn something from this document about target entity using 
        whatever other information I have about entity?
    \end{itemize}
  \item \textbf{Relevance}
    \begin{itemize}
      \item \textbf{Garbage:} not relevant, e.g.\ spam.
      \item \textbf{Neutral:} Not relevant, i.e.\ no info could be deduced about entity, 
        e.g., entity name used in product name, or only pertains to community of target 
        such that no information could be learned about entity, although you can see how 
        an automatic algorithm might have thought it was relevant.
      \item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive 
        implications, or topics or events of likely
        impact on entity.
      \item \textbf{Central:} Relates directly to target such that you would cite it in 
        the WP article for this entity, e.g.\ entity is a
        central figure in topics/events.

@@

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain WP or Twitter entities 
(wiki/twitter URLs) and certain relations of interest (given in
Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (
hence, slot filling). This can be used to automatically populate knowledgebases 
such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. 
Below, you can view some examples of what it means to fill in a slot value; in 
each example there is a sentence of interest that we wish to extract slot values 
from, an entity that the slot value is related to, and a slot name which can be 
thought of as the topic of the slot value:

@@

\noindent In \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus.
In Table~\ref{table:slotNameOntology} you can view some slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems 
that most closely match the changes in the ground truth time line of slot values. 
This is done by searching for other documents that mentioned an entity and exactly 
matched the slot fill strings selected by the assessors.
